---
output:
  html_document: default
  pdf_document: default
---
# FYP Data Analysis with MLR
```{r}
library(dplyr)
library(readr)
CIRP <- read_csv("/Users/defamily/Downloads/CIRP - DATA COLLECTION (Responses) - Form Responses 1.csv")
```
## Removing excluded criteria responses
```{r}
CIRP_clean <- CIRP %>% 
  filter(`What is your Nationality?` != "Non-Malaysian", 
         `Have you played ONE (1) video game with loot box/gacha features in the past 3 months?` != "No",
          `Have you opened at least ONE (1) loot box/gacha in the past 3 months?` != "No")

View(CIRP_clean)
```

## Removing columns
```{r}
CIRP_clean <- CIRP_clean[, -c(1, 2)]

## Reverse scoring columns 
### Define columns to reverse
reverse_cols = c("2. When I am upset I often act without thinking",
                 "5. In the heat of an argument, I will often say things that I later regret",
                 "6. I quite enjoy taking risks",
                 "7. When overjoyed, I feel like I can't stop myself from going overboard",
                 "9. I often make matters worse because I act without thinking when I am upset",
                 "10. I generally seek new and exciting experiences and activities",
                 "11. I tend to act without thinking when I am really excited",
                 "13. I welcome new and exciting experiences and sensations, even if they are a little frightening and unconventional",
                 "15. When I am very happy, I feel like it is OK to give into cravings or overindulge")
```

## Reverse code
```{r}
CIRP_clean[ , reverse_cols] = 5 - CIRP_clean[ , reverse_cols]
```

### Data edit
```{r}
data.frame(colnames(CIRP_clean))

CIRP_clean <- CIRP_clean[, -c(65)]
```

## Compile scorings for each scales and subscales
```{r}
CIRP_clean$M1 <- rowSums(CIRP_clean[,c("1. For the excitement of seeing what will be inside","2. To get items or characters I find visually appealing",
                                       "3. To get items or characters that make me feel good about myself","4. Because I like the feeling of winning when I get something good or rare",
                                       "5. To try and get something personally valuable to me","6. Because it’s fun")], na.rm=TRUE)

CIRP_clean$M2 <- rowSums(CIRP_clean[,c("7. To get past a hurdle or sticking point in the game",
                                       "8. To get items or characters that will be useful or give me an advantage","9. Because I’ve had a failure or defeat in the game")], na.rm=TRUE)

CIRP_clean$M3 <- rowSums(CIRP_clean[,c("10. Because my friends encourage or pressure me to", "11. So that I don’t get shamed or made fun of",
                                       "12. Because I don’t want to feel left out")], na.rm=TRUE)

CIRP_clean$M4 <- rowSums(CIRP_clean[,c("13. Because I am bored", "14. Because I can't stop myself",
                                       "15. Because I get an urge to open them", "16. To take my mind off the real world or my day-to-day life")], na.rm=TRUE)

CIRP_clean$M5 <- rowSums(CIRP_clean[,c("17. To support good causes", "18. To support the developer")], na.rm=TRUE)

CIRP_clean$M6 <- rowSums(CIRP_clean[,c("19. Because there is an in-game event taking place",
                                       "20. To get items or characters I’m collecting", "21.  Because I don’t want to miss the chance to get a limited time item or offer")], na.rm=TRUE)

CIRP_clean$M7 <- rowSums(CIRP_clean[,c("22. To try and win items that I can make gaming currency out of", "23. To try and win items that I can make real money out of")], na.rm=TRUE)

CIRP_clean$IP <- rowSums(CIRP_clean[,c("1. I usually think carefully before doing anything","2. When I am upset I often act without thinking",
                         "3. I generally like to see things through to the end", "4. My thinking is usually careful and purposeful",
                         "5. In the heat of an argument, I will often say things that I later regret", "6. I quite enjoy taking risks",
                         "7. When overjoyed, I feel like I can't stop myself from going overboard", "8. Once I start a project, I almost always finish it",
                         "9. I often make matters worse because I act without thinking when I am upset","10. I generally seek new and exciting experiences and activities",
                         "11. I tend to act without thinking when I am really excited", "12. I am a productive person who always gets the job done",
                         "13. I welcome new and exciting experiences and sensations, even if they are a little frightening and unconventional",
                         "14. Before making up my mind, I consider all the advantages and disadvantages", "15. When I am very happy, I feel like it is OK to give into cravings or overindulge")], na.rm=TRUE)

CIRP_clean$GC <- rowSums(CIRP_clean[,c("1.  I will never be able to stop gambling", "2. A series of losses will provide me with a learning experience that will help me win later",
                                       "3. I’m not strong enough to stop gambling", "4. Specific numbers and/or colours help me win", "5. There are certain circumstances or situations that increase my chances of winning",
                                       "6. My desire to gamble is so overpowering", "7. Gambling makes me happier", "8. Gambling makes the future seem brighter",
                                       "9. My gambling wins prove that I have skills and knowledge related to gambling", "10. I collect specific objects that help increase my chance of winning",
                                       "11. I have specific rituals and behaviors that increase my chance of winning", "12. Gambling makes things seem better")], na.rm=TRUE)

CIRP_clean$RLB <- rowSums(CIRP_clean[,c("1. The thrill of opening Loot Boxes has encouraged me to buy more.","2. I frequently play games longer than I intend to, so I can earn Loot Boxes.",
                                        "3. I have put off other activities, work, or chores to be able to earn or buy more Loot Boxes.", "4. Once I open a Loot Box, I often feel compelled to open another.",
                                        "5.  I have bought more Loot Boxes after failing to receive valuable items")], na.rm=TRUE)
```

# Checking MLR assumptions
```{r}
library(tidyverse)
library(broom)

gacha.model <- lm(RLB ~ M1 + M2 + M3 + M4 + M5 + M6 + M7 + IP + GC, data = CIRP_clean)
summary(gacha.model)

par(mfrow=c(2,2))
plot(gacha.model)
```

## Data Linearity
```{r}
plot(gacha.model,1)
```
## Normality of residuals (QQ plot)
```{r}
plot(gacha.model,2)
```
## Outliers (standard residuals > 3) and High Leverage points
```{r}
plot(gacha.model,3) # Homoscedasticity 
plot(gacha.model,4) 
plot(gacha.model,5)
```
## Cook's distance outliers
```{r}
cooksD <- cooks.distance(gacha.model)
influential <- cooksD[(cooksD > (3 * mean(cooksD, na.rm = TRUE)))]
observed_outliers <- names(influential)
observed_outliers
```
### Remove outliers from dataframe
```{r}
outliers <- as.numeric(observed_outliers)
CIRP2 <- CIRP_clean[-outliers, ]
```
## Check for multivariate outliers
### Subset the independent variables (predictors) used in the model
```{r}
predictors <- CIRP2[, c("M1", "M2", "M3", "M4", "M5", "M6", "M7", "IP", "GC")]
```

### Compute Mahalanobis distance
```{r}
mahal_dist <- mahalanobis(predictors, colMeans(predictors), cov(predictors))
```
### View the Mahalanobis distances
```{r}
mahal_dist
```

## Identify outliers w/ chi-square distribution
```{r}
cutoff <- qchisq(0.98, df = ncol(predictors)) # 99% confidence level
outliers <- which(mahal_dist > cutoff)
outliers
```

## Removing MD outlier
```{r}
CIRP2 <- CIRP2[-outliers, ]
```

# New model
```{r}
gacha.model <- lm(RLB ~ M1 + M2 + M3 + M4 + M5 + M6 + M7 + IP + GC, data = CIRP2)
summary(gacha.model)

sigma(gacha.model)/mean(CIRP2$RLB)
```
### Check beta coefficients
```{r}
install.packages("lm.beta")
library("lm.beta")
lm.beta(gacha.model)
lm(data.frame(scale(gacha.model$model)))
```

# Visualization
```{r}
library(ggplot2)
library(reshape2)

gacha.model %>%
  augment() %>%
  melt(measure.vars = c("M1", "M2", "M3", "M4", "M5", "M6", "M7", "IP", "GC"), variable.name = c("IV")) %>%
  ggplot(., aes(x = value, y = RLB)) +
  geom_smooth(method = "lm") +
  facet_wrap(~IV, scales = "free_x")
```

